volunteer_analysis

### 2022-04-10 code/analysis_code/results.Rmd
figures + calculations

This tells us that there is a significant difference between the MP concentrations in rivers and tributaries! Cool! We can try to tweak this boxplot figure to display those statistics, perhaps.

>>>>

This tells us that there is a significant difference between the MP concentrations in rivers and tributaries! Cool! We can try to tweak this boxplot figure to display those statistics, perhaps. 
# more figures for main rivers vs tribs
```{r}
body %>% ggplot(aes(x = date, y = particles_l, color = body, group = body)) + 
  geom_point() + geom_path() + scale_color_discrete(name = "Water Body")+ 
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  labs(title = "Water Body Microplastic Concentration Over Time", x = "Water Body", y = "Particles/Liter") + scale_x_discrete(labels=c("Fall 2020",
                            "Winter 2021",
                            "Spring 2021",
                            "Summer 2021"))+ 
  ylim(0,300) #removing outliers to better visualize majority of concentrations
```

### 2022-04-10 code/analysis_code/volunteer.Rmd
figures + calculations

The average overall coefficient of variation is 58 for volunteer-counted results.

>>>>

The average overall coefficient of variation is 58 for volunteer-counted results. 
# CV bw A and B for July
```{r}
sample_july <- sampledata %>% filter(date == "july_21") # remove July samples (counted by volunteers, not by self)

july <- sample_july %>% select(a_count, b_count)
matrix_sample <- data.matrix(july)

july <- july %>% mutate(cv = (Rfast::rowcvs(matrix_sample, ln = FALSE)*100))

mean(july$cv)
median(july$cv)
```

#CV for each sample date
```{r}
#november
sample_nov <- sampledata %>% filter(date == "nov_20")

nov <- sample_nov %>% select(a_count, b_count)
matrix_sample <- data.matrix(nov)

nov <- nov %>% mutate(cv = (Rfast::rowcvs(matrix_sample, ln = FALSE)*100))

mean(nov$cv)
median(nov$cv)

#february
sample_feb <- sampledata %>% filter(date == "feb_21")

feb <- sample_feb %>% select(a_count, b_count)
matrix_sample <- data.matrix(feb)

feb <- feb %>% mutate(cv = (Rfast::rowcvs(matrix_sample, ln = FALSE)*100))

mean(feb$cv)
median(feb$cv)

#april
sample_april <- sampledata %>% filter(date == "apr_21") # remove July samples (counted by volunteers, not by self)

april <- sample_april %>% select(a_count, b_count)
matrix_sample <- data.matrix(april)

april <- april %>% mutate(cv = (Rfast::rowcvs(matrix_sample, ln = FALSE)*100))

mean(april$cv)
median(april$cv)
```
